---
title: "Florida Coastal Everglades R Workshop"
author: "Swamp Pirate"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
---
<style>

.navbar-brand {
  display: grid;
  margin: auto;
  padding: 5px;
}

.navbar-author {
  margin-left: 0px;
}

.custom-title {
   font-weight: bold;
   font-size: 14px;
   text-align: left;
}

</style>
```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(plotly)
library(ggplot2)
library(leaflet)
library(mapview)
library(dygraphs)
library(sf)

plot_color <- "Dark2"
today_date <- format(Sys.time(), "%a %b %d %X %Y")

previuos_day <- Sys.Date() - 1

today <- format(today_date, format = "%B %d, %Y")
# ****IMPORTANT: This range is updated on an annual basis*****
prev_wy_year_range <- as.Date(c("2023-01-01", "2023-12-31"))
wy_year_range <- as.Date(c("2024-01-01", "2024-12-31"))


month_range <- seq(as.Date(Sys.Date() - 29), length = 2, by = "1 month")

week_range <- seq(as.Date(Sys.Date() - 7), length = 2, by = "1 week")
area_flow_range <- seq(as.Date(Sys.Date() - 60), length = 2, by = "2 months")
day_range <- seq(as.Date(Sys.Date() - 1), length = 2, by = "1 day")
day_start <- day_range[1]
day_end <- day_range[2]
month_start <- month_range[1]
month_end <- month_range[2]
week_start <- week_range[1] ##CORRECT
week_end <- week_range[2]
coeff <- 10
coeff2 <- 100
```
# Hydrology

## Row
### Information

Note: <span style="color: black; font-size:16px;">The information below along with associated graphics was generated using provisional data and it is subject to change.</span>

- [DBHYDRO Insights](https://apps.sfwmd.gov/dbhydroInsights/#/homepage){target="_blank"}
- [EDEN](https://sofia.usgs.gov/eden/index.php){target="_blank"}
- [Florida Coastal Everglades](https://fcelter.fiu.edu/){target="_blank"}

### Interactive Plot Instructions

- All graphs are interactive, with information on the station on a particular day
- **Zoom in on the y-axis:** Point and drag up or down. To exit, double-click on the plot.
- **Zoom in on the x-axis:** Point and drag left or right. To exit, double-click on the plot.

### Example of Dashboards

- [Lake Okeechobee Watershed Dashboard](https://rpubs.com/SFWMD/1224195){target="_blank"}
- [Water Quality Engagement Project](https://spontaneous-pika-80a117.netlify.app/){target="_blank"}

## Row
### <span class="custom-title">Study Sites</span> Last updated: `r today_date`

```{r}
library(terra)
library(mapview)
library(leafpop)

sites <- read_rds("sites.rds")
sites_sf <- st_as_sf(sites, coords = c("X_NAD83", "Y_NAD83"), crs = 26917)

mapview(sites_sf,
        zcol = "landscape",
        col.regions = c("S" = "blue", "WP" = "green"),
        map.types = c("OpenStreetMap.DE"),
        label = sites_sf$PLOT, 
        popup = popupTable(sites_sf,
                           zcol = c("landscape", "PLOT")),
        burst = FALSE,
        legend = TRUE)

```
## Row
### <span class="custom-title">Water surface Elevation</span> Last updated: `r today_date`
```{r}

library(plotly)

hydro_monthly <- read_rds("hydro_month.rds")

quad_model <- lm(wse_mean ~ poly(TimeIndex, 2, raw = TRUE), data = hydro_monthly)

r2_value <- summary(quad_model)$r.squared

coefs <- coef(quad_model)
eq <- sprintf("y = %.4f x² + %.4f x + %.4f", coefs[3], coefs[2], coefs[1])

y_min <- min(hydro_monthly$wse_mean, na.rm = TRUE) - 5  
start_date <- as.Date("2005-01-01")
end_date <- as.Date("2024-04-30")


# ggolot -> plotly
p <- ggplot(hydro_monthly, aes(x = YearMonth, y = wse_mean)) +
  geom_point(size = 2.5) +   
  geom_line() + 
  geom_errorbar(aes(ymin = wse_mean - wse_sd, ymax = wse_mean + wse_sd), width = 10) +
  geom_smooth(method = "lm", formula = y ~ poly(x, 2, raw = TRUE), se = FALSE, linetype = "dashed") +
  annotate("text", x = as.Date("2015-06-01"), y = y_min,
           label = sprintf("r² = %.2f\n%s", r2_value, eq),
           size = 4, hjust = 0) +
  labs(x = "Year", y = "Water Surface Elevation (cm)", title = "Mean Monthly WSE") +
  scale_x_date(date_breaks = "1 year", date_labels = "%Y") +
  theme_classic() +
  theme(
    panel.border = element_rect(colour = "black", fill = NA, size = 0.5),
    axis.text.x = element_text(angle = 45, hjust = 1)
  )


ggplotly(p)

```

## Row
### <span class="custom-title">Water surface Elevation using dygraphs</span> Last updated: `r today_date`
```{r}
library(plotly)

hydro_monthly <- read_rds("hydro_month.rds")

quad_model <- lm(wse_mean ~ poly(TimeIndex, 2, raw = TRUE), data = hydro_monthly)

r2_value <- summary(quad_model)$r.squared

coefs <- coef(quad_model)
eq <- sprintf("y = %.4f x² + %.4f x + %.4f", coefs[3], coefs[2], coefs[1])

y_min <- min(hydro_monthly$wse_mean, na.rm = TRUE) - 5  
start_date <- as.Date("2005-01-01")
end_date <- as.Date("2024-04-30")

hydro_select <- hydro_monthly %>%
  dplyr::select(YearMonth, wse_mean)

dygraphs::dygraph(hydro_select) %>%
  dySeries("wse_mean",
           label = "water surface elevation",
           stepPlot = TRUE,
           color = "blue") %>%
  dyAxis("y",
         label = "wse (cm)",
         axisLabelColor = "black") %>%
  dyLegend(show = "always",
           hideOnMouseOut = FALSE,
           width = 400) %>%
  dyRangeSelector(height = 10)

```
# Data Table
## Row
### <span class="custom-title">Dataset</span> Last updated: `r today_date`
```{r}
library(DT)

sites <- read_rds("sites.rds")
datatable(sites)
```
